Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-12-12 peakcharacterization_manuscript.Rmd
trying to use png with cairo output
slight reworking of issues w/ lasso models

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

@@

FT-MS data from the Thermo-Fisher Orbitrap instrument used to acquire the data does not provide any information about the raw frequency data. 
Outside of the meta-data, it merely contains the M/Z and intensity values for profile spectra acquired across multiple scans. 
However, the frequency can be calculated by dividing the average M/Z of two adjacent points by their difference (Figure XA, red points reresenting the average M/Z of two adjacent points, red lines representing the difference between the two adjacent points). 
The subsequent differences in frequency should be relatively constant with respect to M/Z, in contrast to the differences of adjacent M/Z points, as shown in Figure XB and XC. 
The Thermo Fusion instrument from which most of our collaborators data has been acquired, at a resolution of 400K, has a mode of 0.5, as shown in Figure XC and XD. 
Restricting to those points that fall into a narrow range of frequency differences (0.49 - 0.51), a model of frequency to M/Z can be generated (see Methods), an example of which is shown in Figure XE. 
This model seems to fit the known relationship between frequency and M/Z, where the frequency is related to $1/\sqrt{mz}$. 
This is useful, because some of the subsequent steps in our workflow use sliding and tiled windows where it is assumed that the sliding windows contain the same number of data points. 
M/Z point-to-point differences are not constant, but can be approximated by a lasso linear model. 
However, it is very difficult to create a lasso model with an intercept of 0, and then vary the width of sliding windows according to the M/Z difference at a particular M/Z. 
Frequency based points suffer none of these drawbacks, and the conversion from M/Z can be derived from the raw profile level data itself, which is incredibly useful.

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dpi = 600, dev = "png", dev.args = list(type = "cairo"))
```

@@

FT-MS data from the Thermo-Fisher Orbitrap instrument used to acquire the data does not provide any information about the raw frequency data. 
Outside of the meta-data, it merely contains the M/Z and intensity values for profile spectra acquired across multiple scans. 
However, the frequency can be calculated by dividing the average M/Z of two adjacent points by their difference (Figure XA, red points reresenting the average M/Z of two adjacent points, red lines representing the difference between the two adjacent points). 
The subsequent differences in frequency should be relatively constant with respect to M/Z, in contrast to the differences of adjacent M/Z points, as shown in Figure XB and XC. 
The Thermo Fusion instrument from which most of our collaborators data has been acquired, at a resolution of 400K, has a mode of 0.5, as shown in Figure XC and XD. 
Restricting to those points that fall into a narrow range of frequency differences (0.49 - 0.51), a model of frequency to M/Z can be generated (see Methods), an example of which is shown in Figure XE. 
This model seems to fit the known relationship between frequency and M/Z, where the frequency is related to $1/\sqrt{mz}$. 
This is useful, because some of the subsequent steps in our workflow use sliding and tiled windows where it is assumed that the sliding windows contain the same number of data points. 
M/Z point-to-point differences are not constant, but can be approximated by a lasso linear model; however, it is very difficult to create a lasso model with an intercept of 0.
In addition, we would also need to vary the width of sliding windows according to the M/Z difference at a particular M/Z based on the lasso model.
Frequency based points suffer none of these drawbacks, and the conversion from M/Z can be derived from the raw profile level data itself, which is incredibly useful.
